Archive Your Project

### 2024-11-26 archive.qmd
Add reference
Provide some advice on finding a suitable repository

Additional guidance is provided by @Daquin2023 and @Garijo2022.

>>>>

Additional guidance is provided by @Daquin2023, @Garijo2022, and @ScienceEurope2021. You can use the registry of research data repositories [re3data.org](https://www.re3data.org/) to find one that matches your criteria. We think that the [Software Heritage code archive](https://www.softwareheritage.org/) and [Zenodo](https://zenodo.org/) are good choices, but don't forget to also check your local institutions for recommendations.
